---
title: "Basic Data Preprocessing"
author: "Phankawee Mukdaprakorn"
date: "25 March 2024"
output:
  html_notebook: default
  pdf_document: default
  html_document:
    df_print: paged
---

## **Setup**

```{r Seting up, warning=False}
library(kableExtra)
library(magrittr) #to be able to execute pipe-operator
library(readr) #to read .csv file
library(dplyr) #to manipulate data
library(here) #to automate setting the working directory
```


## **Data Description**

This dataset has been collected by Los Angeles Police Department(LAPD) since 2020. It demonstrates the crime incidents in Los Angeles. However, because it is digitalised from hard-copied reports which have been stored for long time, there may be some missing information in some rows. This dataset can be downloaded from data.lacity.org (2024) as a `.csv` file.

The dataset consists of 28 fields but for the purpose of this assignment, it will be subset into 18 fields which are explained below:

* **DR_NO** : This field is an unique number of each incident report called "Division of Records Number". The first two-digit indicates the year when the incident is reported, following by the area ID in Los Angeles and 5 more digits to make it unique.
* **Date Rptd** : This field shows the date when the incident is reported.
* **DATE OCC**      This field demonstrates the date when the incident occurs.
* **AREA NAME** : This field shows the place of the police Stations among 21 area in LAPD which has been reported the incident.
* **Rpt Dist No** : This code indicates the sub-area where the incident occurs.  
* **Crm Cd Desc** : This field is the description of the crime code 1 which is considered the most prioritized crime from each incident.
* **Vict Age** : This field shows number of age of the victim in the case.
* **Vict Sex** : This field shows the victim's gender in the case. F, M, and X stand for female, male, and unknown, respectively.
* **Vict Descent** : This presents the descent of the victim.
* **Premis Cd** : This code indicates the type of the location where the incident occurs.
* **Premis Desc** : This field describes the location where the incident occurs.
* **Weapon Desc** : This is a broad description of the weapon which is used in the crime.
* **Status Desc** : This field shows the status of the incident.
* **Crm Cd 1**      This field indicates the primary crime occured in the incident.
* **Crm Cd 2** : This field indicates the less serious crime which happen in the incident compared to Crm Cd1.
* **Crm Cd 3** : This field indicates the less serious crime which happen in the incident compared to Crm Cd1 and Crm Cd2.
* **LOCATION** : This field show the address where the crime incident occur.
* **Cross Street** : This field shows the cross street by the address near the location where the incident takes place.


## **Read/Import Data**

```{r Importing}
setwd(here())
path <- "https://www.dropbox.com/scl/fi/moekhj57kbo1qy6q5rvdj/Crime_Data_from_2020_to_Present.csv?rlkey=qg97ery60gfkmy2srco7zq5y3&st=rfu12prs&dl=1"
crime <- read_csv(path, col_names = TRUE, col_select = c("DR_NO","Date Rptd","DATE OCC","AREA NAME","Rpt Dist No","Crm Cd Desc","Vict Age","Vict Sex","Vict Descent","Premis Cd","Premis Desc","Weapon Desc","Status Desc","Crm Cd 1","Crm Cd 2","Crm Cd 3","LOCATION","Cross Street"))
```

Putting the file path within the `path` variable first does not only make it more convenience, but also easier to read and understand the process. I read my `.csv` raw data file using `read_csv` from *`readr`* package. I also set the argument `col_select()` to specify only the fields that I would like to import which are 18 columns that I mentioned above in this report. I, then, named my dataset "**`crime`**" as its related topic.

## **Inspect and Understand**

```{r}
dim(crime)
colnames(crime)
head(crime,5)
```

I used `dim()` to see the dimension of my **`crime`** dataset. I also check the column names using `colnames()` to confirm the right columns I have imported. After that, I used `head()` to take a glance at first 5 rows of my dataset.

```{r}
str(crime)
```

I also used `str()` to see the structure of my data. There are 917,707 records (I have downloaded this dataset on 18/03/2024) and 18 imported columns. And by using `read_csv()`, R will try to guess types of the data while importing. As be seen in the output from `str()`, it can be shown that there are some columns that need to be converted their datatypes.

#### **Type Conversion**

```{r}
crime$DR_NO <- as.integer(crime$DR_NO)
crime$`Date Rptd` <- as.Date(crime$`Date Rptd`,"%m/%d/%Y")
crime$`DATE OCC` <- as.Date(crime$`DATE OCC`, "%m/%d/%Y")
crime$`AREA NAME` <- as.factor(crime$`AREA NAME`)
crime$`Rpt Dist No` <- as.factor(crime$`Rpt Dist No`)
crime$`Crm Cd Desc`<- as.factor(crime$`Crm Cd Desc`)
crime$`Vict Age` <- as.integer(crime$`Vict Age`)
crime$`Vict Sex` <- crime$`Vict Sex` %>% factor(.,
                                                levels = c("M","F","X"),
                                                labels = c("Male","Female","Unknown"))
crime$`Vict Descent` <- as.factor(crime$`Vict Descent`)
crime$`Premis Cd` <- as.integer(crime$`Premis Cd`)
crime$`Premis Desc` <- as.factor(crime$`Premis Desc`)
crime$`Weapon Desc` <- as.factor(crime$`Weapon Desc`)
crime$`Status Desc` <- as.factor(crime$`Status Desc`)
crime$`Crm Cd 1` <- as.integer(crime$`Crm Cd 1`)
crime$`Crm Cd 2` <- as.integer(crime$`Crm Cd 2`)
crime$`Crm Cd 3` <- as.integer(crime$`Crm Cd 3`)
```

I converted some columns' datatypes because of the reasons listing below:

* **DR_NO** : This field should be read as an integer because it is the unique number of the incident without the character inside. I used `as.integer()` to convert it.
* **Date Rptd** : Date report column had been read as a character at first. I changed its datatype to be date using `as.Date()` function and also, change the format by setting an argument inside the function to be `%m/%d/%Y` which I applied after reading a blog post from Indigo(2011). I chose to remove the time from the format because all rows are all the same as a default value in the system `12:00:00 AM`.
* **DATE OCC** : For this column, I proceeded the same operation as I did with **Date Rptd**.
* **AREA NAME** : As mentioned earlier in this report, area names indicate only 21 police stations in the area so this field can be considered as a categorical variable using `as.factor()` function.
* **Crm Cd Desc** : This one as well, can be a categorical variable because they are all same descriptions describing the crime codes.
* Vict Age    This variable should be read as an integer, not double variable. Thus, I converted it using `as.integer()` function.
* **Vict Sex** : This column should be a categorical variable so I converted it using `factor()` function. In addition, I renamed the value inside from "M","F","X" to be "Male", "Female", and "Unknown", respectively, just to make it easier to understand by setting the argument inside `labels = c("Male","Female","Unknown")`. However, I left the value "H" as N/A since there is no description about it. Unlike "X" is described as "Unknown" in the description from the data source website
* **Vict Descent** : This column shows the descent of the victim so its datatype should be nominal, not just only character. Thus, I used `as.factor()` to convert it.
* **Premis Cd** : This should be read as integer since it is the code without an alphabet inside so I converted it using `as.integer()`.
* **Premis Desc**, **Weapon Desc**, **Status Desc** : They are identically the broad and short descriptions described the code in the system so they should be read as categorical variables. Thus, I used `as.factor()` to convert them.
* **Crm Cd 1**, **Crm Cd 2**, **Crm Cd 3** : They are all a four-digit integer code indicating the type of crime. Thus, they should be read as integer so I used `as.integer()` to convert it.

```{r Checking the level of factor variables}
crime$`AREA NAME` %>% levels()
crime$`Vict Sex` %>% levels()
```
I rechecked some converted fields in my dataset using `levels()` function. However, there is no ordinal variable nor logical variable in my selected dataset.

## **Subsetting** 

```{r}
New_Matrix <- crime %>% slice_head(.,n=10) %>% as.matrix()
class(New_Matrix)
typeof(New_Matrix)
```

I used the `pipe operator` to subset my data as the following steps:

1. I tried to use `slice_head()` function in from *`dplyr`* after finding ways to see the tops of the data apart from using `head()`. After reading the blog post from Moe(2010), I found out many ways of doing it so I chose to try `slice_head()` instead of using `head()` in this case. I put my **`crime`** dataset inside the `slice_head()` function and set `n=10` to get the first 10 rows of my data.
2. After I got my first 10 rows from my dataset using `slice_head()`, I used `as.matrix()` function to convert my dataframe to be matrix and named it **`New_Matrix`**.
3. Then, I used `class()` to make sure that after step 2, **`New_Matrix`** is a matrix. Moreover, I proceeded by using `typeof()` function to check my matrix's datatype.

It is a character because even though at first, there are various datatypes in the dataset, when converting into the matrix, all datas must be the same datatype so `as.matrix()` converted them to be all character before putting them into the matrix named **`"New_Matrix"`**.

## **Create a new Data Frame**

```{r}
My_df <- data.frame(StudentID = as.integer(round(runif(10)*10000)),
                    Grade = factor(sample(c("A","B","C","D"),size = 10,replace = TRUE),levels = c("D","C","B","A"), ordered = TRUE))
```
   
I first created my new data frame by designing it into 2 columns which are:

* **StudentID** : This field indicates 10 random four-digit integers as a student ID of each record. I used `runif()` to generate random numbers between 0 to 1, then time 10,000 and used `round()` to get four-digit numbers. After that, I used `as.integer()` to make sure that those set of random numbers are integer. I adapted the way of using `runif()` to generate random numbers from reading from Cookbook for R website(n.d.)
* **Grade** : For this column, I designed it to represent the grade of each record. I, first, used `sample()` by determining `size=10` and `replace = TRUE` in order to get 10 random grades among A, B, C, D. Secondly, I put that function into `factor()` to factorize those random grades. In this process, I also set `levels = c("D","C","B","A")` and make this dataset an ordinal variable by set `ordered = TRUE`.

I used `data.frame()` with those two vectors to create the new dataframe and store it as **`My_df`**.
   
```{r}
class(My_df$StudentID)
class(My_df$Grade)
str(My_df)
```
I tried to recheck the datatypes of both field in my new dataframe using `class()` and `str()`. As be seen from the output, there are four levels in my ordinal variable (**Grade**) which are `"D"<"C"<"B"<"A"`.

```{r}
weight_vect <- round(runif(10,min = 40,max = 80),digits = 2)
class(weight_vect)
```

According to the instruction, I created a new numeric vector called `weight_vect` using the similar methodology as when creating `StudentID`, but this time, I set the range of the number between 40-80 just to make it more realistic, assuming that students weigh between 40 to 80 kilograms.

```{r}
My_df <- cbind(My_df, weight_vect)
My_df
```

I combined the new numeric vector `weight_vec` with **`My_df`** using `cbind()` and get 3 variables in my new dataset **`My_df`**. I printed **`My_df`** to check the result showing that there are 3 variables in the dataset.


## **References**
Bache S, Wickham H (2022). _magrittr: A Forward-Pipe Operator for R_. R package version 2.0.3, <https://CRAN.R-project.org/package=magrittr>.

Data.lacity.org (Department LAP) (2024) _Crime Data from 2020 to Present_ [data set], Data.lacity.org website, accessed 18 March 2024. https://data.lacity.org/Public-Safety/Crime-Data-from-2020-to-Present/2nrs-mtv8/about_data

_Generating random numbers_, (n.d.) Cookbook for R website, accessed 20 March 2024. http://www.cookbook-r.com/Numbers/Generating_random_numbers/

Indigo (16 September 2011) 'Changing date format in R', _Stackoverflow_, accessed 19 March 2024. https://stackoverflow.com/questions/7439977/changing-date-format-in-r

Moe (19 April 2010) 'Select first 4 rows of a data.frame in R', _Stackoverflow_, accessed 19 March 2024. https://stackoverflow.com/questions/2667673/select-first-4-rows-of-a-data-frame-in-r

R Core Team (2024). _R: A Language and Environment for Statistical Computing_. R Foundation for Statistical Computing, Vienna, Austria. <https://www.R-project.org/>.

Taheri S (2024) 'Module 2 Notes Get: Importing, Scraping and Exporting Data with R' [Course Website], Royal Mlebourne Institute of Technology, 124 La Trobe St, Melbourne VIC 3000.

Taheri S (2024) 'Module 3 Notes Understand: Understanding Data and Data Structures' [Course Website], Royal Mlebourne Institute of Technology, 124 La Trobe St, Melbourne VIC 3000.

Wickham H, François R, Henry L, Müller K, Vaughan D (2023). _dplyr: A Grammar of Data Manipulation_. R package version 1.1.4, <https://CRAN.R-project.org/package=dplyr>.

Wickham H, Hester J, Bryan J (2024). _readr: Read Rectangular Text Data_. R package version 2.1.5, <https://CRAN.R-project.org/package=readr>.

Zhu H (2024). _kableExtra: Construct Complex Table with 'kable' and Pipe Syntax_. R package version 1.4.0, <https://CRAN.R-project.org/package=kableExtra>.



<br>
<br>
